Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-02-03 paper.tex
some discussion added

\newcommand{\bjoern}[2]{{\color{blue}{{\bf #1} #2}}}
\newcommand{\ahfx}{\ensuremath{\alpha_\text{HFX}}\xspace}

@@

@@

>>>>

\newcommand{\bjoern}[2]{{\color{blue}{{\bf #1} #2}}}
\newcommand{\Zhong}[2]{{\color{purple}{{\bf #1} #2}}}
\newcommand{\ahfx}{\ensuremath{\alpha_\text{HFX}}\xspace}

@@

\Zhong{}{It is worth noting that in multiscale modeling there is usually correlations between the site energies $E_i$. 
Those correlations are due to electrostatic interactions, while the distribution $P(\log_{10}(\tau))$ evaluated from the Monte Carlo sampling does not take the energy correlations into account.
However, in the case of MADN, these correlations are notably absent. This can be attributed to the specific molecular arrangement and electronic structure of MADN, which effectively decouples the site energies from one another. As a result, the site energies in MADN are practically uncorrelated, simplifying the analysis of their contributions to the time-of-flight distribution. }

@@

\Zhong{}{The decrease in the confidence intervals of $\log_{10}(\mu)$ indicates a reduction in the relative uncertainty in charge mobility, so a higher fields lead to a more deterministic mobility values.
There some possible physical reasons for such reduction in uncertainty. At low electric fields, the charge carriers spend a significant amount of time in some low-energy sites which are generated in the Monte Carlo sampling. 
As the field strength increases, the drift term becomes more dominant, reducing the impact of these stochastic factors.

Furthermore, a stronger electric field help the carrier to escape from the low energy sites more efficiently. This effect would reduce variability in observed mobilities, contributing to a narrowing confidence interval.
So a stronger applied field, which is deterministic, results in a more predictable mobility response, therefore reducing the spread in $\log_{10}(\mu)$ distribution.
}
